{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-05-02 bmvc_review.tex
Comments Answered

In summary, the scale filter, $R_{s}$, is designed to directly handle
the scale change of a target and provides $R_{t}^{L}$ and $R_{t}^{S}$
with more focused ROIs about the target's translation. A translation
filter, $R_{t}^{L}$, is intended to look at a larger search area to
estimate the target's translation and recover from any potential
drifts. Another translation filter, $R_{t}^{S}$, on the other hand, is
designed to addresses the drawback of $R_{t}^{L}$ that it may learn
noisy shape features due to its large search area. Figure
\ref{Workflow_figure_EnKCF} illustrates the workflow of the proposed
algorithm and alg.\ref{alg:MKCF} shows the pseudo-code of {\it
  E}nKCF. In the following section, we will briefly mention the theory
behind the KCF.

@@

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
To verify the usefulness of our algorithm, we choose two public,
available datasets:
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and
UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footage of 123 objects. We aims
at developing an object tracking algorithm that ``efficiently'' runs
in ``high speed,'' $\ge 300$ fps. Given this goal, we believe that the
UAV123 video data is a better fit in evaluating the performance of the
proposed algorithm. This is because there are many challenging scenes,
e.g., abrupt scale/illumination changes as all the targets were
recorded from bird-eye view. Although we are primarily interested in
developing an algorithm for mobile, embedded robotic applications, it
is important to compare the performance of the proposed algorithm with
those of the state-of-the-art in nominal dataset for comparison. To
this end, we chose the OTB100 data that contains the videos recorded
from smart phones and typical cameras in perspective view.

{\it Burak: What does this mean?}  Finally, the {\it E}nKCF2 is tested
on temporally downsampled version of UAV123 dataset.

\textbf{Finding Optimal Hyperparameters} Each of three KCFs in {\it
  E}nKCF is designed for addressing a specific challenge of a single,
target tracking problem. Thus each of them should have different value
for the optimal parameters. For instance, the primary task of the
translation filter, $R_{t}^{L}$ is to estimate the translation of a
target from the previous frame whereas the scale filter, $R_{s}$ and
the estimated state of the particle filter are primarily used to
estimate the scale and translation. Because of this, we set the
learning rates ($\beta$) of individual filters, $R_{t}^{L}$,
$R_{t}^{S}$, and $R_{s}$ differently as $0.020$, $0.020$ and
$0.010$.

{\it Burak: This is a dangling sentence.} The desired response and
hanning window for each KCF is shown in fig.~\ref{fig:Filters}.

For the kernel of the Gaussian neighboring function, we empirically
found the optimal values of $\alpha$ as $0.6$, $0.4$, and $0.4$ for
$R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$, and the learning rate as $0.12$
for $R_{t}^{L}$.

{\it Burak: Did we even mention whether $R_{t}^{L}$ runs on every
  frame? This might confuse others because all I remembered is we use
  each of KCFs at every other $k$ or $n$ frames.}

For the particle filter implementation, we found $1000$ is the optimal
number of particles,

{\it Burak: ?}
and use the \textit{efficient number of samples}
metric shown below to determine whether we need to perform importance
re-sampling or not to keep reasonable variance.

@@

@@

The success rate metric counts how many outputs from a tracking
algorithm successfully overlap with those of the ground truth greater
than a given threshold. The overlap is specifically computed by the
Intersection-Over-Union (IoU) between a tracking output and that of
the ground truth. Given the number of the correct frames based an IoU
threshod, the success rate is the ratio of the correct frames to the
number of the total frames for testing.

@@

We compare our tracker to some other high-speed ($\geq$300 fps)
state-of-the-art trackers including KCF\cite{henriques2015high}, CSK
\cite{henriques2012exploiting}, STC\cite{zhang2014fast},
MOSSE\cite{bolme2010visual,henriques2015high}. Also, some relatively
lower-speed ($\geq$50) trackers are used to evaluate the robustness of
the proposed trackers. These trackers include SAMF\cite{li2014scale},
DSST\cite{danelljan2014accurate}, LCT\cite{ma2015long},
MEEM\cite{zhang2014meem} and Struck\cite{hare2012efficient}.
Fig.~\ref{fig:UAV123_DATASET} shows the results on the UAV123
dataset.

>>>>

In summary, the scale filter, $R_{s}$, is designed to directly handle
the scale change of a target and provides $R_{t}^{L}$ and $R_{t}^{S}$
with more focused ROIs about the target's translation. A translation
filter, $R_{t}^{L}$, is intended to look at a larger search area to
estimate the target's translation and recover from any potential
drifts. Another translation filter, $R_{t}^{S}$, on the other hand, is
designed to addresses the drawback of $R_{t}^{L}$ that it may learn
noisy shape features due to its large search area. Figure
\ref{Workflows} illustrates the workflow of the proposed
algorithm and alg.\ref{alg:MKCF} shows the pseudo-code of {\it
  E}nKCF. We do not have a seperate pseudeo-code for {\it E}nKCF2 as there are only two differences between 
  {\it E}nKCF and {\it E}nKCF2. First, the {\it E}nKCF2 runs $R_{t}^{L}$ every frame
to better tackle large ego-motion at low video frame rates. Second, we remove the particle filter in the {\it E}nKCF2 
tracker due to large ego-motion. In the following section, we will briefly mention the theory
behind the KCF.

@@

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
To verify the usefulness of our algorithm, we choose two public,
available datasets:
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and
UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footage of 123 objects. We aims
at developing an object tracking algorithm that ``efficiently'' runs
in ``high speed,'' $\ge 300$ fps. Given this goal, we believe that the
UAV123 video data is a better fit in evaluating the performance of the
proposed algorithm. This is because there are many challenging scenes,
e.g., abrupt scale/illumination changes as all the targets were
recorded from bird-eye view. Although we are primarily interested in
developing an algorithm for mobile, embedded robotic applications, it
is important to compare the performance of the proposed algorithm with
those of the state-of-the-art in nominal dataset for comparison. To
this end, we chose the OTB100 data that contains the videos recorded
from smart phones and typical cameras in perspective view. Finally, the {\it E}nKCF2 is tested
on temporally down-sampled version of the UAV123 dataset which is named UAV123$\_$10fps dataset.

\textbf{Finding Optimal Hyperparameters} Each of three KCFs in {\it
  E}nKCF is designed for addressing a specific challenge of a single,
target tracking problem. Thus each of them should have different value
for the optimal parameters. For instance, the primary task of the
translation filter, $R_{t}^{L}$ is to estimate the translation of a
target from the previous frame whereas the scale filter, $R_{s}$ and
the estimated state of the particle filter are primarily used to
estimate the scale and translation. Because of this, we set the
learning rates ($\beta$) of individual filters, $R_{t}^{L}$,
$R_{t}^{S}$, and $R_{s}$ differently as $0.020$, $0.020$ and
$0.010$. The desired template response and hanning window for each KCF is shown in fig.~\ref{fig:Filters}.
For the kernel of the Gaussian neighboring function, we empirically
found the optimal values of $\alpha$ as $0.6$, $0.4$, and $0.4$ for
$R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$, and the learning rate as $0.12$
for $R_{t}^{L}$.

We tuned the number of particles in the particle filter to $1000$ after carrying out experiments, 
The re-sampling is only performed when the \textit{efficient number of samples} (eq.~\ref{eq:Neff_PF}) is lower than a
pre-defined threshold. This way, we can continuously keep reasonable variance among particles.
\begin{equation}
	\hat{N}_{eff} \approx \dfrac{1}{\sum_{p=1}^{P}w_{p}^{2}}
	\label{eq:Neff_PF}
\end{equation}

@@

{\it YoungWoo : Trackers are ranked in the legend in the graphs - the numbers next 
to each tracker is precision at 20 px and AUC for the success rate. It is how people rank
trackers in precision and success plots. I agree with you that we can have an additional table. Let me know what
you think about it now.}

@@

The success rate metric counts how many outputs from a tracking
algorithm successfully overlap with those of the ground truth greater
than a given threshold. The overlap is specifically computed by the
Intersection-Over-Union (IoU) between a tracking output and that of
the ground truth. Given the number of the correct frames based an IoU
threshod, the success rate is the ratio of the correct frames to the
number of the total frames for testing.  In the success rate plots, trackers are
ranked based on AUC scores.

@@

{\it YoungWoo :  I thought we were going to do that tomorrow. I have generated figures and 
I can easily remove any ones. SRDCF and MEEM are the top two as of now. I am working on removing them as of now. Please 
consider that we do not have SRDCF and MEEM while you are editing the results section.}

We compare our tracker to other high-speed ($\geq$300 fps)
state-of-the-art trackers including KCF\cite{henriques2015high}, CSK
\cite{henriques2012exploiting}, STC\cite{zhang2014fast},
MOSSE\cite{bolme2010visual,henriques2015high}. Also, some relatively
lower-speed ($\geq$50) trackers are used to evaluate the robustness of
the proposed trackers. These trackers include SAMF\cite{li2014scale},
DSST\cite{danelljan2014accurate}, MEEM\cite{zhang2014meem}, Struck\cite{hare2012efficient}, and SRDCF\cite{danelljan2015learning}.
Fig.~\ref{fig:UAV123_DATASET} shows the results on the UAV123
dataset.
